---
title: "Senior Project"
author: "Calvin Davis"
date: "10/24/2021"
output: word_document
---

```{r}
library(ggplot2)
library(tidyr)
library(ggpubr)
library(dplyr)
library(lme4)

setwd("~/Senior Project")
```


```{r}
calibration_data <- read.csv("Thermocouple calibration data.csv", header = TRUE)
thermocouple_05_10 <- read.csv("05-10-2021 Thermocouple data.csv", header = TRUE)
thermocouple_data <- read.csv("Thermocouple Data.csv", header = TRUE)
collection_data <- read.csv("Collection Data.csv", header = TRUE)
aquaflux_data <- read.csv("AquaFluxData.csv", header = TRUE)

```




##Hi Savannah :) I will do my best to lay out what I have been struggling with:
##The first challenge I have been struggling with is just the layout of the thermocouple data. More specifically, it is spread out across 5 different csv files in which I have had to manually identify/match which thermocouple was used and to what lizard it belongs to. The next challenge is that due to the nature of our methods, there is a different amount of temperature data for each lizard (varies by a few seconds on average) but implies that the data does not exactly align with the CEWL timeseries. Lastly, because my experience of writing my own functions in R is quite limited, I have been unsure as how to automate the process of applying calibration curves to the thermocouple data. More specifically, I would love a function that identifies which thermocouple was used, automatically apply the proper calibration equation, and then reformat the newly calibrated data so it properly aligns with the the CEWL data set and so far I am having a hard time even begining a function like this. All that being said, these above steps are things I find fairly easy to do in excel (which I know you said is not ideal) so I will now try to annotate further the above challenges with the actual data sets...



##I first created calibration curves for each thermocouple via linear regressions of the reference temperature x thermocouple temperature data, and did that for each individual thermocouple (which in I realized I'm not sure is even the proper way to do this and is certainly not the most efficient)
Thermocouple E
```{r}
regression_e <- lm(calibration_data$reference_temp1~calibration_data$Value_E) #calculate regression curve
coef(regression_e) #prints coeffiencts to manually make regression curve
```
## y =  1.011570x - 1.641703

Thermocouple B
```{r}
regression_b <- lm(calibration_data$reference_temp1~calibration_data$Value_B)
coef(regression_b)
```
## y = 1.018007x - 1.671978

Thermocouple H
```{r}
regression_h <- lm(calibration_data$reference_temp1~calibration_data$Value_H)
coef(regression_h)
```
## y =  1.035925x - 1.852796

Thermocouple A
```{r}
regression_a <- lm(calibration_data$reference_temp2~calibration_data$Value_A)
coef(regression_a)
```
## y = 1.010286x - 1.618859

Thermocouple D
```{r}
regression_d <- lm(calibration_data$reference_temp2~calibration_data$Value_D)
coef(regression_d)
```
## y = 1.008465x - 1.621470

Thermocouple F
```{r}
regression_f <- lm(calibration_data$reference_temp2~calibration_data$Value_F)
coef(regression_f)
```
## y = 1.009847x - 1.700887

Thermocouple C
```{r}
regression_c <- lm(calibration_data$reference_temp2~calibration_data$Value_C)
coef(regression_c)
```
## y = 1.005188x - 1.550718     


##I was then trying to figure out a way to automate the application of the above equations by creating a dataframe with the respective information and then somehow applying that but got completely lost
```{r}
#data frame with of calibration curves
   yint <- c(1.641703, 1.671978, 1.852796, 1.618859, 1.621470, 1.700887, 1.550718)
   slope <- c(1.011570, 1.018007, 1.035925, 1.010286, 1.008465, 1.009847, 1.005188)
   couple <- c("E", "B", "H", "A", "D", "F", "C")

calibration_curves <- data.frame(yint, slope, couple)
#split_calibration_curves <- split.data.frame(calibration_curves, f=calibration_curves$couple)

```

```{r}
   #applies calibration equation for E thermocouples
(calibration_curves$slope[1] * ___________ - calibration_curves$yint[1]
 
    #applies calibration equation for B thermocouples
(calibration_curves$slope[2] * ___________ - calibration_curves$yint[2]

   #applies calibration equation for H thermocouples
(calibration_curves$slope[3] * ___________ - calibration_curves$yint[3]
   
   #applies calibration equation for A thermocouples
(calibration_curves$slope[4] * ___________ - calibration_curves$yint[4]
   
   #applies calibration equation for D thermocouples
(calibration_curves$slope[5] * ___________ - calibration_curves$yint[5]
   
   #applies calibration equation for F thermocouples
(calibration_curves$slope[6] * ___________ - calibration_curves$yint[6]
   
   #applies calibration equation for C thermocouples
(calibration_curves$slope[7] * ___________ - calibration_curves$yint[7]

```




##So instead I started thinking about appling the curves manually in excell... which I know I'm not supposed to do but like I said I got lost...

```{r}
##This is what the raw, unmodified thermocouple data looks like for each day: 'vertically oriented', unlabeled, and different amounts of time
OG_05_10_thermocouple_data <- read.csv(
   "Original Format 05-10-2021 Thermocouple data", header = true)
View(OG_05_10_thermocouple_data)

##I was then going to reformat the data into something where I can more easily discern which couple/lizard the data belongs to and then manually apply the calibration curve. As a side note the only way to identify which thermocouple was used is based on comparing chamber in/out or aquaflux data times. The result was Something like this:
thermocouple_05_10 <- read.csv("05-10-2021 Thermocouple data.csv", header = TRUE)
View(thermocouple_05_10)

##I was then going to manually align/cut the calibrated thermocouple data so it fit with the CEWL data, so it would end up looking something like this:
aquaflux_data <- read.csv("AquaFluxData.csv", header = TRUE)
View(aquaflux_data)

```


##This process is obviously not efficient as I would have to do the above steps to each of the data collecttion days individually, which isn't something I mind doing, however I sense it is bad science practive so I would love a point in the write direction. Sorry if any of this wasn't clear either, but hopefully it can be a start





##Thermocouple calibration: regression of reference temp x thermocouple temp
```{r}
ggplot() +
   geom_point(data=calibration_data, 
         aes(x= calibration_data$ï..Place, 
             y = calibration_data$reference_temp1), 
             color = "black") +
   geom_point(data=calibration_data, 
         aes(x=calibration_data$ï..Place, 
             y = calibration_data$Value_E), 
             color = "blue") +
   theme_classic() 
  # scale_x_continuous(limits = c(50,150), breaks=seq(0,150, 10)) 
   
   
```

```{r}
##can be fitted to any of the thermocouples to visualize the calibration curve
ggplot(calibration_data, #graphs thermocouple temp for lead E x reference thermometer temp
      aes(x = Value_C, y = reference_temp2)) +
      geom_point() +
      geom_smooth(method = "lm", se = TRUE) +
      theme_classic() +
      stat_regline_equation() #displays the regression line equation

```



```{r}
initial_pt <- subset(aquaflux_data, Time_sec>119.5 & Time_sec<120.5)
final_pt <- subset(aquaflux_data, Time_sec>=900)


initial_final_cewl <- data.frame(initial_pt$ï..ID,
                                 initial_pt$Flux_g.m2h, 
                                 final_pt$Flux_g.m2h, 
                                 initial_pt$Treatment,
                                 final_pt$Flux_g.m2h - initial_pt$Flux_g.m2h, #Abolsute                                                                                       change
                                 ((final_pt$Flux_g.m2h -     #relative change
                                    initial_pt$Flux_g.m2h)/initial_pt$Flux_g.m2h)*100) 


colnames(initial_final_cewl) <- c('Lizard ID', 
                                  'Initial CEWL', 
                                  'Final CEWL', 
                                  'Treatment', 
                                  'Absolute Change in CEWL', #Final - initial
                                  'Relative Change in CEWL') #Final - initial / initial * 100
```




##Heating/Cooling Rates
##subset by lizard ID and take absolute value for the difference between min and max temp 

```{r}
##Creating temperature change data using minimums and maximums but...

lows <- tapply(subset_cewl$Cloacal_Temp_C, subset_cewl$ï..ID, min, na.rm = TRUE)
highs <- tapply(subset_cewl$Cloacal_Temp_C, subset_cewl$ï..ID, max, na.rm = TRUE)
temp_change <- (highs - lows ) / 13 #this is using the susbetted data (-2min) so its really only over a 13min time scale

temp_rate_values <- data.frame(collection_data$individual_ID,
                               collection_data$treatment,
                               lows, highs, temp_change)

colnames(temp_rate_values) <- c('Lizard ID', 
                                  'Treatment', 
                                  'Minimum Temperature (C)', 
                                  'Maximum Temperature (C)',
                                  'Temp Rate of Change (C/min)')


##Need to come up with a better way to do this (final - initiial) becuase current method doesn't show increase/decrease in temperature and is completely wrong for control values



```

```{r}
ggplot() +
       aes(temp_rate_values$Treatment, 
           temp_rate_values$`Temp Rate of Change (C/min)`, 
           fill = temp_rate_values$Treatment) +
       geom_boxplot() +
       theme_classic() +
       scale_fill_manual(values = c("Control" = "forestgreen",
                                "Cooling" = "steelblue3",  
                                "Heating"="orange")) + 
   labs(x= "Mass (g)" , y= "Change in CEWL", color ="Treatment") 
      # scale_y_continuous(trans = "log10") + #transforms to log scale
       #scale_x_continuous(limits = c(0,38), breaks=seq(0,40, 5))
```



##Would it be better to show an average heating/cooling rate in terms of a linear regression?
```{r}
##graphing temperature change over the entire 15 minute period

ggplot(aquaflux_data) +
       aes(aquaflux_data$Time_sec, 
           aquaflux_data$Cloacal_Temp_C, 
           color = aquaflux_data$Treatment) +
       geom_point(size = 0.01) +
       geom_smooth(method = "lm", se = TRUE, aes(color = aquaflux_data$Treatment), na.rm = TRUE) +
       theme_classic() +
       scale_color_manual(values = c("Control" = "forestgreen",
                                     "Cooling" = "steelblue3",  
                                     "Heating"="orange")) +
       labs(x= "Time (sec)" , y= "Temperature", color ="Treatment", se = FALSE) +
       scale_y_continuous(trans = "log10")  #transforms to log scale
       #scale_y_continuous(limits = c(0,40), breaks=seq(0,40, 5))  #transforms to log scale
       #scale_x_continuous(limits = c(120,950), breaks=seq(0,950, 50)) ```

```

```{r}
temp_rates_reg <- lm(aquaflux_data$Cloacal_Temp_C ~ aquaflux_data$Time_sec + aquaflux_data$Treatment)

summary(temp_rates_reg)
```

```{r}
coef(temp_rates_reg)
```



```{r}
##Creating temp data using the initial & final temp point data but...

change_in_temp <- (final_pt$Cloacal_Temp_C - initial_pt$Cloacal_Temp_C)


temp_data <- data.frame(initial_pt$ï..ID, 
                        initial_pt$Treatment,
                        initial_pt$Cloacal_Temp_C,
                        final_pt$Cloacal_Temp_C,
                        change_in_temp, 
                        change_in_temp/13)

colnames(temp_data) <- c('Lizard ID',
                         'Treatment',
                         'Initial Temp (C)',
                         'Final Temp (C)',
                         'Change in Temp',
                         'Rate of Temp Change (C/min)')

##Missing 4 values: 416 & 418 that lack calibration data, 428 & 429 are missing one or both of initial/final temp points due to starting thermocouple lack and data shortage

```


```{r}
ggplot(temp_data) +
       aes(temp_data$`Change in Temp`,
           initial_final_cewl$`Relative Change in CEWL`,
           color = temp_data$Treatment) +
       geom_point(size = 3) +
       theme_pubclean() +
       scale_color_manual(values = c("Control" = "forestgreen",
                                     "Cooling" = "steelblue3",  
                                     "Heating"="orange")) +
       labs(x= "Change in Temp", 
            y= "Relative Change in CEWL (%)", 
            color ="Treatment", se = FALSE) 
     #  scale_x_continuous(limits = c(-2,2), breaks=seq(-2,2, 0.5))

       
```




##CEWL Data


##Raw Plot of all data
```{r}
ggplot(aquaflux_data) +
       aes(aquaflux_data$Time_sec, 
           aquaflux_data$Flux_g.m2h, 
           color = aquaflux_data$Treatment) +
       geom_point(size = 0.01) +
       theme_classic() +
       scale_color_manual(values = c("Control" = "forestgreen",
                                     "Cooling" = "steelblue3",  
                                     "Heating"="orange")) +
       labs(x= "Time (sec)" , y= "Flux (g/m^2hr)", color ="Treatment", se = FALSE) +
      # scale_y_continuous(trans = "log10") + #transforms to log scale
       scale_x_continuous(limits = c(120,950), breaks=seq(0,950, 50)) 
      
       

       #geom_smooth( 
           # aes(aquaflux$Time_sec, aquaflux$Flux_g.m2h, color = aquaflux$Treatment, method = "lm")) 
      # scale_x_continuous(limits = c(0,16), breaks=seq(0,20, 2)) +
       #scale_y_continuous(limits = c(0,7), breaks=seq(0,7, 1))
      #alpha = number controls transparency
```

```{r}
lizard_ID <- as.factor(aquaflux_data$ï..ID)
```




```{r}
##Want a graph where all lines start at same y-intercept, maybe with residuals from a line at log = _____? but am having a hard time with where to start



```



##Average CEWL
```{r}
subset_cewl <- aquaflux_data[ which( aquaflux_data$Flux_g.m2h >0 & aquaflux_data$Time_sec >120),]
#eliminate first 2 minutes of data as ambient air is eliminated
sub_id <- as.factor(subset_cewl$ï..ID)

```

```{r}
#finding the average CEWL for each treatment
average_cewl <- data.frame(
                   tapply(subset_cewl$Flux_g.m2h, subset_cewl$ï..ID, mean), #average CEWL /                                                                                         lizard
                   collection_data$treatment # assigning lizards treatment
)

colnames(average_cewl) <- c('avg_cewl', 'Treatment')
average_cewl <- tibble::rownames_to_column(average_cewl, "Lizard_ID")
```

```{r}
##average CEWL for each lizard
ggplot() +
   aes(average_cewl$Lizard_ID, average_cewl$avg_cewl, fill = average_cewl$Treatment) +
   geom_col() +
   theme_classic() +
   scale_fill_manual(values = c("Control" = "forestgreen",
                                 "Cooling" = "steelblue3",  
                                 "Heating"="orange")) +
   labs(x= "Lizrd ID" , 
        y= "CEWL (g/m^2hr)", 
        fill ="Treatment") 
```

```{r}
##boxplots to show average CEWL by treatment group after removing first 2 minutes of data to account for intake of ambient air
 ggplot() +
   aes(x = average_cewl$Treatment, 
       y = average_cewl$avg_cewl, 
       fill = average_cewl$Treatment) +
   geom_boxplot() +
   theme_classic() +
   scale_fill_manual(values = c("Control" = "forestgreen",
                                "Cooling" = "steelblue3",  
                                "Heating"="orange"))  +
   scale_y_continuous(limits = c(0,40), breaks=seq(0,40, 5)) +
   labs(x= "Treatment" , y= "Average CEWL (g H2O/m^2hr)", fill ="Treatment") 
```

```{r}
avg_cewl_aov <- aov(average_cewl$avg_cewl~average_cewl$Treatment)

summary(avg_cewl_aov)

TukeyHSD(avg_cewl_aov)
```



##Average Change in CEWL
##Change in CEWL = end pt CEWL - begining pt CEWL
```{r}
initial_pt <- subset(aquaflux_data, Time_sec>119.5 & Time_sec<120.5)
final_pt <- subset(aquaflux_data, Time_sec>=900)


initial_final_cewl <- data.frame(initial_pt$ï..ID,
                                 initial_pt$Flux_g.m2h, 
                                 final_pt$Flux_g.m2h, 
                                 initial_pt$Treatment,
                                 final_pt$Flux_g.m2h - initial_pt$Flux_g.m2h, #Abolsute                                                                                       change
                                 ((final_pt$Flux_g.m2h -     #relative change
                                    initial_pt$Flux_g.m2h)/initial_pt$Flux_g.m2h)*100) 


colnames(initial_final_cewl) <- c('Lizard ID', 
                                  'Initial CEWL', 
                                  'Final CEWL', 
                                  'Treatment', 
                                  'Absolute Change in CEWL', #Final - initial
                                  'Relative Change in CEWL') #Final - initial / initial * 100
```

```{r}
##absolute change in CEWL (final - initial CEWL) by treatment group, based on first and last data points after removing first 2 minutes of data
ggplot() +
   aes(x = initial_final_cewl$Treatment, 
       y = initial_final_cewl$`Absolute Change in CEWL`, 
       fill = initial_final_cewl$Treatment) +
   geom_boxplot() +
   theme_classic() +
   scale_fill_manual(values = c("Control" = "forestgreen",
                                "Cooling" = "steelblue3",  
                                "Heating"="orange"))  +
   labs(x= "Treatment" , y= "Absolute Change in CEWL (g H2O/m^2hr)", fill ="Treatment") 
```

```{r}
change_cewl_aov <- aov(initial_final_cewl$`Absolute Change in CEWL`~initial_final_cewl$Treatment)

summary(change_cewl_aov)

TukeyHSD(change_cewl_aov)
```

```{r}
##Relative change in CEWL (final - initial CEWL)/initial * 100 by treatment group, based on first and last data points after removing first 2 minutes of data
ggplot() +
   aes(x = initial_final_cewl$Treatment, 
       y = initial_final_cewl$`Relative Change in CEWL`, 
       fill = initial_final_cewl$Treatment) +
   geom_boxplot() +
   geom_point() +
   theme_classic() +
   scale_fill_manual(values = c("Control" = "forestgreen",
                                "Cooling" = "steelblue3",  
                                "Heating"="orange"))  +
   labs(x= "Treatment" , y= "Relative Change in CEWL (%)", fill ="Treatment") 
```

```{r}
change_cewl_aov <- aov(
               initial_final_cewl$`Relative Change in CEWL` ~ initial_final_cewl$Treatment)

summary(change_cewl_aov)

TukeyHSD(change_cewl_aov)
```




##For the life of me I can't seem to find any resources to help make a line graph where all CEWL measurements start at the same relative point like we discussed. Any advice here would be greatly apprecieated




##Change in CEWL x Mass
```{r}
##Distribution of masseses for each treatment
ggplot() +
   aes( 
       x = collection_data$mass_g,
       fill = collection_data$treatment) + 
   geom_histogram(position = "dodge", 
                  binwidth = 1, 
                  breaks = seq(7, 20, by = 1), 
                  color = "black") +
   theme_classic() +
   scale_fill_manual(values = c("Control" = "forestgreen",
                                "Cooling" = "steelblue3",  
                                "Heating"="orange")) + 
   labs(x= "Mass (g)" , y= "Count", fill ="Treatment") +
   scale_y_continuous(limits = c(0,4), breaks=seq(0,4, 1)) +
   scale_x_continuous(breaks = seq(0, 20, by = 1))
```

```{r}
##Change in CEWL with Mass
ggplot() +
   aes(x = collection_data$mass_g,
       y = initial_final_cewl$`Relative Change in CEWL`,
       color = collection_data$treatment) + 
   geom_point() +
   geom_smooth(method = "lm", se=TRUE) +
   theme_classic() +
   scale_fill_manual(values = c("Control" = "forestgreen",
                                "Cooling" = "steelblue3",  
                                "Heating"="orange")) + 
   labs(x= "Mass (g)" , y= "Change in CEWL", color ="Treatment") 
   #scale_y_continuous(limits = c(0,4), breaks=seq(0,4, 1)) +
   #scale_x_continuous(breaks = seq(0, 20, by = 1))
```

```{r}
##Distribution of SVL's for each treatment
ggplot() +
   aes(x = collection_data$treatment, 
       y = collection_data$SVL_mm,
       fill = collection_data$treatment) + 
   geom_boxplot() +
   theme_classic() +
   scale_fill_manual(values = c("Control" = "forestgreen",
                                "Cooling" = "steelblue3",  
                                "Heating"="orange"))  +
   labs(x= "Treatment" , y= "SVL(mm)", fill ="Treatment") +
    scale_y_continuous(limits = c(0,80), breaks=seq(0,80, 5))
```

```{r}
##Change in CEWL with SVL
ggplot() +
   aes(x = collection_data$SVL_mm,
       y = initial_final_cewl$`Relative Change in CEWL`,
       color = collection_data$treatment) + 
   geom_point() +
   geom_smooth(method = "lm", se=TRUE) +
   theme_classic() +
   scale_color_manual(values = c("Control" = "forestgreen",
                                "Cooling" = "steelblue3",  
                                "Heating"="orange")) + 
   labs(x= "SVL (mm)" , y= "Change in CEWL", color ="Treatment") 
   #scale_y_continuous(limits = c(0,4), breaks=seq(0,4, 1)) +
   #scale_x_continuous(breaks = seq(0, 20, by = 1))
```


```{r}
names(aquaflux_data)
```



##CEWL x TEMP
```{r}
##With first 2 minutes
ggplot(aquaflux_data) +
       aes(aquaflux_data$Cloacal_Temp_C, 
           aquaflux_data$Flux_g.m2h, 
           color = aquaflux_data$Treatment) +
       geom_point(size = 0.01) +
       theme_classic() +
       scale_color_manual(values = c("Control" = "forestgreen",
                                     "Cooling" = "steelblue3",  
                                     "Heating"="orange")) +
       labs(x= "Temp (C)" , y= "Flux (g/m^2hr)", color ="Treatment", se = FALSE) +
      # scale_y_continuous(trans = "log10") + #transforms to log scale
       scale_x_continuous(limits = c(0,38), breaks=seq(0,40, 5)) 
```


```{r}
##without first 2 minutes
ggplot() +
       aes(subset_cewl$Cloacal_Temp_C, 
           subset_cewl$Flux_g.m2h, 
           color = subset_cewl$Treatment) +
       geom_point(size = 0.01) +
       theme_classic() +
       scale_color_manual(values = c("Control" = "forestgreen",
                                     "Cooling" = "steelblue3",  
                                     "Heating"="orange")) +
       labs(x= "Temp (C)" , y= "Flux (g/m^2hr)", color ="Treatment", se = FALSE) +
      # scale_y_continuous(trans = "log10") + #transforms to log scale
       scale_x_continuous(limits = c(0,38), breaks=seq(0,40, 5)) 
```













##Mixed Linear Model
##random effect: lizard ID
##individual variation: temperature, (SVL, mass, body condition), capture climate, ambient temp/humidity(?)
##Should I be using change in temperature??



##"a two-sided linear formula object describing both the fixed-effects and random-effects part of the model, with the response on the left of a ~ operator and the terms, separated by + operators, on the right. Random-effects terms are distinguished by vertical bars (|) separating expressions for design matrices from grouping factors. Two vertical bars (||) can be used to specify multiple uncorrelated random effects for the same grouping variabl"


```{r}
ggplot(aquaflux_data) +
       aes(aquaflux_data$Time_sec, 
           aquaflux_data$Flux_g.m2h, 
           color = aquaflux_data$Treatment) +
       geom_point(size = 0.01) +
       theme_classic() +
       scale_color_manual(values = c("Control" = "forestgreen",
                                     "Cooling" = "steelblue3",  
                                     "Heating"="orange")) +
       labs(x= "Time (sec)" , y= "Flux (g/m^2hr)", color ="Treatment", se = FALSE) +
      # scale_y_continuous(trans = "log10") + #transforms to log scale
       scale_x_continuous(limits = c(120,950), breaks=seq(0,950, 50)) 
```


```{r}
ggplot() +
       aes(subset_cewl$Time_sec, 
           subset_cewl$Flux_g.m2h, 
           color = subset_cewl$Treatment) +
       geom_point(size = 0.01) +
       theme_classic() +
       scale_color_manual(values = c("Control" = "forestgreen",
                                     "Cooling" = "steelblue3",  
                                     "Heating"="orange")) +
       labs(x= "Temp (C)" , y= "Flux (g/m^2hr)", color ="Treatment", se = FALSE) 
      # scale_y_continuous(trans = "log10") + #transforms to log scale
      # scale_x_continuous(limits = c(0,38), breaks=seq(0,40, 5)) 
```


```{r}
View(collection_data)
```


```{r}
x <- collection_data$individual_ID
print(x)
```

```{r}
##need to find a way to incorporate collection data into aquaflux/subset_cewl data. 
##I want to create a function/loop which identifies the lizard ID in the collection data dataset and pull the svl & mass data from that dataset to then apply it to tge aquaflux/subset_cewl dataset so its in 'vertical' fornat so its easier to work with for the mixed model


for (id in 401:439) {
   
   x <- collection_data[id,]
   
   print(x)
   
}


```

```{r}
for (id in 401:439) {
   
   if(x == subset_cewl$ï..ID) {}
}
```



```{r}
if(collection_data$individual_ID == subset_cewl$ï..ID) {
   
   subset_cewl$mass <- collection_data$mass_g
}
```






```{r}
cewl_basic <- lm(subset_cewl$Flux_g.m2h ~ subset_cewl$Time_sec)
summary(cewl_basic)
```

```{r}
plot(cewl_basic, which = 1)
```
```{r}
plot(cewl_basic, which = 2)
```


```{r}
cewl_treatment <- lm(subset_cewl$Flux_g.m2h ~ subset_cewl$Time_sec + subset_cewl$Treatment)
summary(cewl_treatment)
```

```{r}
library(lme4)
```
```{r}
names(subset_cewl)
```


```{r}
##fixed effects: time and treatment and cloacal temp(?), anbient humidity/temp?
##random effects: Lizard ID nested in Day, 



cewl_mml <- lmer(data = subset_cewl,
                 Flux_g.m2h ~ Time_sec + 
                 Treatment + 
                 Amb_temp_C + 
                 Amb_humidity_. + 
                 Mass_g + 
                 SVL_mm
                 Cloacal_Temp_C +
                 (1|ï..ID) )
summary(cewl_mml)
```


```{r}
drop1(cewl_mml)
```


```{r}
plot(cewl_mml, which = 1)
```
```{r}
plot(cewl_mml, which = 2)
```



